Medical Concept Extraction

### 2012-12-14 paper/paper.tex
Updates to the paper.
Adding the abstract to the paper.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

% preprint + pagenumbering for page numbers
\documentclass[preprint]{style}
\pagenumbering{arabic}

@@

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. \cite{Wagner73}

@@

@@

\subsection{n-gram Features}

@@

>>>>

\documentclass[preprint]{style}
\pagenumbering{arabic}

@@

This paper presents a system for extracting medical concepts from patients' hospital records. Hospitals and medical practices are increasingly switching to electronic medical records. This trend has opened the doors to exciting applications for Natural Language Processing in medical and biological fields. One such application is concept extraction: identifying a high level semantic labels in a body of text. Concept extraction on medical records is useful in automating analysis tasks that would otherwise have to be done manually. For example, hospital administrators may want to tabulate what medications are being prescribed the most, insurance companies may want to ensure that patients receive proper care and are billed accordingly for fraud detection and auditing purposes, and government agencies may be interested in exploring and better understanding public health trends.

In service of that end, we present an algorithm and system that is capable of classifying words in medical records across four different medically-relevant categories. This is useful in and of itself to end users wishing to analyze medical records but is also useful in supporting other higher-level NLP and learning systems. This paper describes the system's design, implementation, and performance when tested on set of 500 pre-annotated medical records from Boston-area hospitals.

@@

\subsection{N-gram Features}

@@

\subsection{Stemming}

Our CRF F1 scores went from 0.58 to 0.82

@@

\item Include that PNG image from easy.py
